A Study on Common Bug Fix Patterns in Rust

### 2022-10-12 sections/related.tex
instructions in related work

Weimer et al.~\cite{forrest2009genetic,nguyen2009using} developed GenProg, a program repair tool that uses genetic programming. The main idea behind this tool is that statements follow certain patterns in a codebase. Therefore, if we can find the correct version of a faulty statement somewhere in the program. This tool showed promising results as it managed to find patches without any additional annotations or human involvements.

@@

@@

The main intuition in pattern-based program repair methods is that the bug fixing modifications of the programs follow certain patterns. Thus, prior study of the common bug fix patterns is a crucial step for developing these repair tools. Pan et al. \cite{pan2009toward} analyzed seven large-scale widely used Java projects and obtained 27 common bug fix patterns. Though they did the analysis on Java projects, their reported patterns were not specific to Java. Martinez and Monperrus \cite{martinez2015mining} \cite{martinez2012mining} exploited the frequency of observed patterns to introduce a heuristic patch searching method. In their empirical evaluation, they concluded that the probabilistic values for repair actions can help with reducing the search space, hence creating a more effective repair tool.

Hanam et al. \cite{hanam2016discovering} conducted a similar research but for finding Javascript most pervasive bug fix patterns. They presented a large-scale study of the most common bug fix patterns by mining 105K commits from 134 server-side JavaScript projects. They used DBSCAN clustering algorithm and divided bug fixing change types into 219 clusters, from which they extracted 13 pervasive cross-project bug fix patterns.

@@

@@

>>>>

Weimer et al.~\cite{forrest2009genetic,nguyen2009using} developed GenProg, a program repair tool that uses genetic programming. The main idea behind this tool is that statements follow certain patterns in a codebase. Therefore, if we can find the correct version of a faulty statement somewhere in the program. This tool showed promising results as it managed to find patches without any additional annotations or human involvements.
% the sentence starting with "therefore" lacks a verb

@@

% replace this next paragraph with some text about how search based program repair depends on patterns, and we have patterns that we have found to be used in actual repairs. That should go at the top of 5.1.

% say why you're talking about GenProg etc.

% fix the citations

@@

% say why pattern-based repair is different from search-based repair
The main intuition in pattern-based program repair methods is that the bug fixing modifications of the programs follow certain patterns. Thus, prior study of the common bug fix patterns is a crucial step for developing these repair tools. Pan et al. \cite{pan2009toward} analyzed seven large-scale widely used Java projects and obtained 27 common bug fix patterns. Though they did the analysis on Java projects, their reported patterns were not specific to Java. Martinez and Monperrus \cite{martinez2015mining} \cite{martinez2012mining} exploited the frequency of observed patterns to introduce a heuristic patch searching method. In their empirical evaluation, they concluded that the probabilistic values for repair actions can help with reducing the search space, hence creating a more effective repair tool.

Hanam et al. \cite{hanam2016discovering} conducted similar research, but for finding JavaScript most pervasive bug fix patterns. They presented a large-scale study of the most common bug fix patterns by mining 105K commits from 134 server-side JavaScript projects. They used the DBSCAN clustering algorithm and divided bug fixing change types into 219 clusters, from which they extracted 13 pervasive cross-project bug fix patterns.

@@

% again, say how we are like or unlike these works

@@

% say how is this related to our work?
